Distributional Trees and Forests

### 2017-12-06 pkg/disttree/inst/draft/draft.Rnw
adapted to changes in ref.bib
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1826 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: e46f6205a2fc840e4d01b0a2634347faa119cebd

%\newpage
\nocite{hothorn2006unbiased, zeileis2008model, hothorn2015partykit, Messner2016, loh2011classification, stasinopoulos2007generalized, Seibold2016, Seibold2017, breiman2001random, stasinopoulos2005, yee2010vgam}
% zeileis2008implementing, 
% zeileis2010party, 
% hothorn2015package,

>>>>

%\newpage
\nocite{hothorn2006unbiased, zeileis2008model, hothorn2015partykit, Messner2016, loh2011classification, stasinopoulos2007generalized, Seibold2016, Seibold2017, breiman2001random, stasinopoulos2005, yee2010vgam, gamboostLSS2016}
% zeileis2008implementing, 
% zeileis2010party, 
% hothorn2015package,
